Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-05-31 Manuscript.Rmd
fixed citation issue and subscript issue

---
title: Apparent preferences for cognitive effort fade when multiple forms of effort
  and delay are interleaved in a foraging environment
author: "Claudio Toro-Serey^1,2^, Gary A. Kane^1,2^, & Joseph T. McGuire^1,2^"
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{float}
- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
- \usepackage{indentfirst}
- \usepackage{fixltx2e}
output:
  pdf_document:
    highlight: haddock
    keep_tex: no
  word_document: #default
    reference_docx: Style_reference_draft.docx
  html_document:
    df_print: paged
csl: apa.csl
indent: true
bibliography: bibliography.bib
---

@@

## Experiment 2: Within-subjects Comparison of Costs

@@

```{r iBIC and parameter comparison (Fig. 9), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling results. A: iBIC values for four candidate models of choice behavior for both experiments. Lower values indicate better fit. B: Estimates of the bias parameter c~demand~ for participants in the Physical, Cognitive, and Wait cost conditions of Experiment 1. Negative values suggest the Cognitive group acted as if cognitive demands attenuated the perceived opportunity cost of the delay. C: Estimates of other model parameters indicated consistent foraging behavior across conditions and experiments. D: Synthetic behavior for Experiment 2 generated by the winning model. Error bars correspond to the empirical mean acceptance rate ± SEM per cost type, whereas lines and shaded areas show the model-generated mean acceptance rate and its SEM, respectively. The model's behavior recapitulated the initial apparent preference for cognitive effort and the eventual convergence of acceptance rates by the end of the session."}
# modelPlot <- (bicPlot + costPlot) / allFitsPlot
# ggsave("./Images/FIG9_modelresult_part.png", modelPlot, device = "png", height = 8, width = 11)
include_graphics("./Images/FIG9_modelresults.png")

@@

```{r New BIC and parameter comparison (Fig. 9), eval = figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling results. A: iBIC values for four candidate models of choice behavior for both experiments. Lower values indicate better fit. B: Estimates of the bias parameter c~demand~ for participants in the Physical, Cognitive, and Wait cost conditions of Experiment 1. Negative values suggest the Cognitive group acted as if cognitive demands attenuated the perceived opportunity cost of the delay. C: Estimates of other model parameters indicated consistent foraging behavior across conditions and experiments. D: Synthetic behavior for Experiment 2 generated by the winning model. Error bars correspond to the empirical mean acceptance rate ± SEM per cost type, whereas lines and shaded areas show the model-generated mean acceptance rate and its SEM, respectively. The model's behavior recapitulated the initial apparent preference for cognitive effort and the eventual convergence of acceptance rates by the end of the session."}
# modelPlot <- (bicPlot + costPlot) / allFitsPlot
# ggsave("./Images/FIG9_modelresult_part.png", modelPlot, device = "png", height = 8, width = 11)
include_graphics("./Images/FIG9_modelresults.png")
```

>>>>

---
title: Apparent preferences for cognitive effort fade when multiple forms of effort
  and delay are interleaved in a foraging environment
author: "Claudio Toro-Serey^1,2^, Gary A. Kane^1,2^, & Joseph T. McGuire^1,2^"
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{float}
- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
- \usepackage{indentfirst}
- \usepackage{fixltx2e}
output:
  pdf_document:
    highlight: haddock
    keep_tex: no
    fig_caption: yes
  word_document: #default
    reference_docx: Style_reference_draft.docx
  html_document:
    df_print: paged
csl: apa.csl
indent: true
bibliography: bibliography.bib
---

@@

## Experiment 2: Within-subject Comparison of Costs

@@

```{r iBIC and parameter comparison (Fig. 9), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling results. A: iBIC values for four candidate models of choice behavior for both experiments. Lower values indicate better fit. B: Estimates of the bias parameter c-demand for participants in the Physical, Cognitive, and Wait cost conditions of Experiment 1. Negative values suggest the Cognitive group acted as if cognitive demands attenuated the perceived opportunity cost of the delay. C: Estimates of other model parameters indicated consistent foraging behavior across conditions and experiments. D: Synthetic behavior for Experiment 2 generated by the winning model. Error bars correspond to the empirical mean acceptance rate ± SEM per cost type, whereas lines and shaded areas show the model-generated mean acceptance rate and its SEM, respectively. The model's behavior recapitulated the initial apparent preference for cognitive effort and the eventual convergence of acceptance rates by the end of the session."}
# modelPlot <- (bicPlot + costPlot) / allFitsPlot
# ggsave("./Images/FIG9_modelresult_part.png", modelPlot, device = "png", height = 8, width = 11)
include_graphics("./Images/FIG9_modelresults.png")

@@

```{r New BIC and parameter comparison (Fig. 9), eval = figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling results. A: iBIC values for four candidate models of choice behavior for both experiments. Lower values indicate better fit. B: Estimates of the bias parameter c-demand for participants in the Physical, Cognitive, and Wait cost conditions of Experiment 1. Negative values suggest the Cognitive group acted as if cognitive demands attenuated the perceived opportunity cost of the delay. C: Estimates of other model parameters indicated consistent foraging behavior across conditions and experiments. D: Synthetic behavior for Experiment 2 generated by the winning model. Error bars correspond to the empirical mean acceptance rate ± SEM per cost type, whereas lines and shaded areas show the model-generated mean acceptance rate and its SEM, respectively. The model's behavior recapitulated the initial apparent preference for cognitive effort and the eventual convergence of acceptance rates by the end of the session."}
# modelPlot <- (bicPlot + costPlot) / allFitsPlot
# ggsave("./Images/FIG9_modelresult_part.png", modelPlot, device = "png", height = 8, width = 11)
include_graphics("./Images/FIG9_modelresults.png")
```
